%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    {\Huge \scshape Shashank Gupta} \\ \vspace{1pt}
    \small \raisebox{-0.1\height}\faPhone\ +1-862-318-1725 $|$ 135 Windsor Street, Kearny, NJ 07032 \\ \vspace{1pt}
     \href{mailto:shashank.and.gupta@gmail.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{shashank.and.gupta@gmail.com}} $|$ 
    \href{https://www.linkedin.com/in/shashank47/}{\raisebox{-0.2\height}\faLinkedin\ \underline{linkedin.com/in/shashank47}} $|$
    \href{https://github.com/Sha661nk}{\raisebox{-0.2\height}\faGithub\ \underline{github.com/Sha661nk}} $|$ \href{https://www.kaggle.com/wrecked22}{\raisebox{-0.1\height}\faKaggle\ \underline{kaggle.com/wrecked22}}
    \vspace{-8pt}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Rutgers Business School}{Sep. 2022 -- Dec 2022}
      {Masters in Information Technology \& Analytics}{Newark \& New Brunswick, NJ}
      
    \resumeSubheading
      {Indian Institute of Technology, Kanpur}{Jul. 2015 -- May 2019}
      {Bachelor of Technology in Electrical Engineering}{Kanpur, UP, India}
  \resumeSubHeadingListEnd

%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, R, SQL, C, C++} \\
     \textbf{Tools}{: Jupyter Notebook, R Studio, Tableau, PostgreSQL, MongoDB, Neo4j, JIRA, MS Excel, LateX, Git \& Github} \\
     \textbf{Frameworks \& Libraries}{: Pandas, NumPy, Scikit Learn, Matplotlib, NLTK, ggplot2, CV2, Seaborn, plotly, pytesseract, Gensim, TensorFlow, OpenCV} \\
    }}
 \end{itemize}
 \vspace{-16pt}

%-----------EXPERIENCE-----------
\section{Work Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Larsen \& Toubro Infotech}{Jul 2019 -- Sep 2022}
      {Senior Data Analyst}{Pune, India}
      \resumeItemListStart
        \resumeItem{Designed data-processing pipelines to automate data cleansing operations, and pushed the cleansed data to the OSI PI-historian database, cutting the manual processing time by 90\%.}
        \resumeItem{Collaborated with three members to devise a pump health monitoring solution to plan the preventive maintenance of the pumps leveraging Python for RUL modeling and Tableau for visualization \& dashboarding.}
        \resumeItem{Trained a Logistic Regression model to predict the steam generator failure, reducing maintenance expenditure by 40\%.}
        \resumeItem{Constructed a Python script to completely automate the process of equipment name extraction from Industrial CAD drawings employing pytesseract and CV2 packages, eliminating manual interventions entirely.}
        \resumeItem{Developed stored procedures and views in SSMS to provide structured data and formulate HTML and ASP .NET scripts for the reports.}
      \resumeItemListEnd

    \resumeSubheading
      {IDEAS - A SAS Company}{May 2019 -- Jul 2019}
      {Data Science Intern}{Pune, India}
      \resumeItemListStart
        \resumeItem{Forecasted the Hotel Prices using the ARIMA model and selected optimal Auto-Regressive lags via BIC \& AIC, helping Boutique Hotels set an optimum price and increasing room occupancy.}
        \resumeItem{Performed descriptive and predictive analysis of hotel pricing data to explore the seasonal trends in business and examined the influence of special events and seasonal trends on estimating hotel prices by model.}
        \resumeItem{Outperformed the previous forecasting model by achieving a 10\% reduction in sMAPE.}
        
    \resumeItemListEnd
    
  \resumeSubHeadingListEnd
\vspace{-16pt}
%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{KYC Automation System} $|$ \emph{Python, .NET, Power BI, \href{https://github.com/Sha661nk/KYC-Automation} {\underline{Github Link}}}}  {Aug 2021}
          \resumeItemListStart
            \resumeItem{Collaborated with a team of four members to develop an end-to-end solution for automating the KYC process, replacing manual interventions completely.}
            \resumeItem{Leveraged a Pre-trained VGG16 model to Validate customer face and Emblem from ID Cards. Retrieved the applicant’s information using Tesseract-OCR and validated the information against the UIDAI DB.}
            \resumeItem{Completed the KYC process within 30 seconds per person and notified the applicant of the KYC status using automated emails.}
          \resumeItemListEnd
          \vspace{-16pt}
      \resumeProjectHeading
          {\textbf{NASA Turbo-Jet Engine Failure Prediction} $|$ \emph{Python, Jupyter-Notebook, \href{https://github.com/Sha661nk/Nasa-Turbo-Jet-Engine-Failure-Prediction} {\underline{Github Link}}}}{Sep 2022}
          \resumeItemListStart
            \resumeItem{Designed and built a failure prediction model for NASA Jet Engines using Logistic Regression, Support Vector Classifier (SVC), and Decision Tree.}
            \resumeItem{Conducted Exploratory data analysis to explore the trends versus the Remaining Useful Life (RUL) of engines.}
            \resumeItem{Utilized the layout editor to create a UI for the application in order to allow different scenes to interact with each other.}
          \resumeItemListEnd 
          \vspace{-16pt}
          \resumeProjectHeading
          {\textbf{IBM Employees Attrition Prediction} $|$ \emph{Python, Jupyter-Notebook, \href{https://github.com/Sha661nk/Attrition-Rate-Prediction} {\underline{Github Link}}}}{Aug 2022}
          \resumeItemListStart
            \resumeItem{Analyzed the root causes of attrition and prepared reports for HR with actionable insights for attrition control via EDA.}
            \resumeItem{Trained a logistic Regression model to predict the employees likely to leave the company.}
            \resumeItem{Achieved an AUROC score of 0.82 and an F1 score of 0.74 while predicting employee attrition.}
          \resumeItemListEnd 
    \resumeSubHeadingListEnd
\vspace{-12pt}

%-----------INVOLVEMENT---------------
\section{Honors \& Awards}
            \resumeItemListStart
                \resumeItem{Received Dean’s MITA Merit Scholarship at Rutgers Business School.}
                \vspace{-2.0mm}
                \resumeItem{Ranked among the top 5\% of Data Scientists in the Kaggle Community.}
                \vspace{-2.0mm}
                \resumeItem{Elected as the Coordinator of DESCON Hobby Group under the Science \& Technology Council, IIT Kanpur.}
                \vspace{-2.0mm}
                \resumeItem{Ranked among the top 2.9\% of students who participated in the Joints Entrance Exam (JEE) - Mains, 2015.}
            \resumeItemListEnd

\end{document}
